\newpage
\chapter{Doctoral Development Progress\label{appendix:b}}
Various activities which work towards the DDP have been completed:
\begin{itemize}
  \item Demonstrated for labs in several taught modules;
  \begin{itemize}
    \item Autumn Semester 14/15
    \begin{itemize}
      \item COM4506 - Testing \& Verification in Safety Critical Systems
    \end{itemize}
    \item Spring Semester 14/15
    \begin{itemize}
      \item COM3420 - Software Hut
      \item COM6102 - Advanced Java Programming
    \end{itemize}
    \item Autumn Semester 15/16
    \begin{itemize}
      \item COM1003 - Java Programming
    \end{itemize}
    \item Spring Semester 15/16
    \begin{itemize}
      \item COM1003 - Java Programming
      \item COM3420 - Software Hut
      \item COM4521 - Parallel Computing with GPUs
    \end{itemize}
  \end{itemize}
  \item Completed the `Small Group Teaching: Laboratory Demonstration' module to develop skills related to working as a graduate teaching assistant, including: teaching and question answering in a laboratory context.
  \item I submitted a paper to AAMAS, although it was not accepted it has provided greater awareness of the procedure for publication in international journals.
  \item Assisted Dr Ramsay Taylor in development of a Java library that undergraduate students have used to interact with the Diamond's Lego robots. This involved developing a simplified wrapper for the lejos library.
  \item Assisted Dr Paul Richmond in proof reading lectures notes and lab materials during the development of the new module COM4521.
  \item Demonstrated during one of the 14/15 outreach sessions for Cuttlers ambassadors program with local school children.
  \item Acted as the student chair of the student staff liaison committee for the academic year of 14/15. This role involved: chairing meetings; assigning actions; attending the learning \& teaching committee; and making contact with relevant members of staff.
  \item I updated the VRGraphics mailing list so that it contains all current members and now continue to maintain this.
  \item I have attended seminars within the research group, however am yet to present one myself.
  \item Acted as student chair of SSLCom for the university year 2014-2015, chaired several meetings delegating actions and contacting relevant persons post-meeting.
  \item 2014-2015 PG Computer Science representative at Faculty level SSLCom.
  \item 2014-current PhD representative at SSLCom, raise concerns of PhD students at meetings.
  %\item Academic website?
  
\end{itemize}